MS Depression Paper

### 2022-08-26 msdepression/scripts/MS_Depression_First_Paper_started_20220728/msdepression_n380_started_20220728.Rmd
Add files via upload

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(visreg)
library(lme4)
library(lmerTest)
library(ggplot2)
library(reshape2)
library(pwr)
library(mgcv)
library(boot)
library(boot.pval)
library(lsr)
#functions
source("~/BBL/msdepression/scripts/msdepression_functions.R")
```

@@

Current ns for people with at least 1 promis score= 
Total n promis scores: 1694 
Total n unique individuals w/promis scores: 501

Different scores have different # of overall scans
                        Total                      General_Health                  Quality_of_Life                  Physical_Health 
                            1694                             1693                             1503                             1503 
          Mental_Health_and_Mood   Social_Activities_Satisfaction   Carrying_Out_Social_Activities Carrying_Out_Physical_Activities 
                            1503                             1503                             1501                             1499 
              Emotional_Problems                  Fatique_Average     PostOp.PROMIS.Physical.Score       PostOp.PROMIS.Mental.Score 
                            1499                             1499                             1440                             1442

W/good mimosa:
Total n promis scores : 398
Total n unique individuals w/promis scores: 116
Total n unique indivs in nondepressed group = 36
Total n unique individuals in depressed group = 46

@@

Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
    1.0   376.8   763.0   873.3  1229.8  2487.0 
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
0.002747 1.035027 2.096154 2.399132 3.378434 6.832418

@@

Proportion:
Proportion within versus outside depression map correlated w/promis scores (33 analyses per group (11 promis domains x 3 networks [total, depression 25%, nondep 75%]))
    - all participants (116)
    - Depressed + nondepressed (82)
    - Non-depressed alone (36)
    - Depressed alone (46)

Proportion of individual fascicle affected related to promis scores (777 analyses per group (11 promis domains x 77 individual fascicles))
  - all participants (116)
  - Depressed + nondepressed (82)
  - Non-depressed alone (36)
  - Depressed alone (46)

@@

Volume within versus outside depression map correlated w/promis scores (33 analyses per group (11 promis domains x 3 networks [total, depression 25%, nondep 75%]))
   - all participants (116)
    - Depressed + nondepressed (82)
    - Non-depressed alone (36)
    - Depressed alone (46)

Volume of individual fascicle affected related to promis scores  (777 analyses per group (11 promis domains x 77 individual fascicles))
  - all participants (116)
  - Depressed + nondepressed (82)
  - Non-depressed alone (36)
  - Depressed alone (46)

Promis results:
Interestingly, across all 11 scores, with the exception of fatigue, Depressed patients have lower scores (lower = worse functioning), than non-depressed patients. controls. They all fdr correct. What I love about this is fatigue not being different. If fatigue was worse in depressed patients, one could argue that quality of life, health, emotional problems, social activities, etc are all worse because of underlying fatigue. Similarly, as fatigue is a component of the PHQ9 and depression screening, this could be confounding. That they were different in a lot of measures but not fatigue is informative.

Quality_of_Life	0.015199144			
Physical_Health	0.012579264			
Mental_Health_and_Mood	0.012579264			
Social_Activities_Satisfaction	0.001063449			
Carrying_Out_Social_Activities	0.011375799			
Carrying_Out_Physical_Activities	0.031616473			
Emotional_Problems	0.011270683			
Fatique_Average	0.231497853			
PostOp.PROMIS.Physical.Score	0.041172446			
PostOp.PROMIS.Mental.Score	0.001253404

Proportion
Proportion within versus outside depression map correlated w/promis scores - NO SIGNIFICANT FINDINGS
    - all participants (116)
    - Depressed + nondepressed (82)
    - Non-depressed alone (36)
    - Depressed alone (46)

Proportion of individual fascicle affected related to promis scores-  NO SIGNIFICANT FINDINGS
  - all participants (116)
  - Depressed + nondepressed (82)
  - Non-depressed alone (36)
  - Depressed alone (46)

Volume     
Volume within versus outside depression map correlated w/promis scores -  NO SIGNIFICANT FINDINGS
   - all participants (116)
    - Depressed + nondepressed (82)
    - Non-depressed alone (36)
    - Depressed alone (46)

Volume of individual fascicle affected related to promis scores-  NO SIGNIFICANT FINDINGS
  - all participants (116)
  - Depressed + nondepressed (82)
  - Non-depressed alone (36)
  - Depressed alone (46)

@@

##########################################################
#            Read in PROMIS Data              #
##########################################################
promis_data <- readRDS(paste0(homedir, "/data/dac/promis_data_cleaned_n1694_unique_indiv_n501_2015-2022.rds"))
promis_score_names <- names(promis_data[7:16])

df_people_with_promis_data <- df_demo_and_fascicles %>%
  filter(EMPI %in% promis_data$EMPI) #n=398

unique_empis_in_promis_group <- unique(df_people_with_promis_data$EMPI) #n=116

```
```{r make_df_with_volume_instead_of_proportion}
#I'll read in the volume of each fascicle, and multiply it by the proportion of volume loss in each subject, thereby returing the volume of the fascicle affected

@@

@@

@@

#sort all the fascicles by %overlap, in decreasing order (so highest overlap at the top), and then take the top 1-quartile
dep_network_names_top_quartile_no_cranial_nerves_by_vol<- (fascicle_values_dep_no_cranial_nerves[order(fascicle_values_dep_no_cranial_nerves$non_zero_voxels_in_dep_map, decreasing = TRUE),])$fascicle[1:quartile] #n=19

dep_network_total_volume_top_quartile_no_cranial_nerves <-
sum(fascicle_volumes_dep_network$num_voxels_total[which(fascicle_volumes_dep_network$fascicle %in% dep_network_names_top_quartile_no_cranial_nerves_by_vol)])

@@

bottom_75_total_volume_no_cranial_nerves <-
sum(fascicle_volumes_dep_network$num_voxels_total[which(fascicle_volumes_dep_network$fascicle %in% dep_network_names_bottom_3_quartiles_no_cranial_nerves_by_vol)])

@@

dep_and_healthy_groups_for_ICD_analysis <- df_demo_and_fascicle_volumes_full %>% 
  filter(depGroupVar != 0)  %>% 
  mutate(total_fascicle_vol_lost = rowMeans(across(fascicle_names_no_cranial_nerves))) %>%
  mutate(total_fascicle_vol_lost_indepnet_top_quartile = 
           rowMeans(across(dep_network_names_top_quartile_no_cranial_nerves_by_vol))) %>%
  mutate(prop_fascicle_vol_lost_indepnet_top_quartile = (total_fascicle_vol_lost_indepnet_top_quartile / dep_network_total_volume_top_quartile_no_cranial_nerves)) %>%
  mutate(total_fascicle_vol_lost_nondep_bottom_3_quartiles = 
           rowMeans(across(dep_network_names_bottom_3_quartiles_no_cranial_nerves_by_vol))) %>%
  mutate(total_fascicle_vol_lost_no_cc = rowMeans(across(fascicle_names_no_cranial_nerves[fascicle_names_no_cranial_nerves!="CC"]))) %>%
  mutate(prop_fascicle_vol_lost_bottom_3_quartile = (total_fascicle_vol_lost_nondep_bottom_3_quartiles / bottom_75_total_volume_no_cranial_nerves)) %>%
  mutate(total_fascicle_vol_lost_indepnet_top_quartile_no_cc = 
           rowMeans(across(dep_network_names_top_quartile_no_cranial_nerves_by_vol[dep_network_names_top_quartile_no_cranial_nerves_by_vol != "CC"]))) %>%
  mutate(total_fascicle_vol_lost_nondep_bottom_3_quartiles_no_cc = 
           rowMeans(across(dep_network_names_bottom_3_quartiles_no_cranial_nerves_by_vol[dep_network_names_bottom_3_quartiles_no_cranial_nerves_by_vol != "CC"]))) %>%
  group_by(EMPI) %>% 
  arrange(EXAM_DATE) %>% 
  slice(1) %>% 
  ungroup()

@@

@@

@@

# geom violin within vs outside depression network
dep_net_group <- c(rep("Dep_net", times = 380), rep("Non_dep_net",times = 380))
net_values <- c(df_mean_fascicle_volumes_and_diagnosis$total_fascicle_vol_lost_indepnet_top_quartile, df_mean_fascicle_volumes_and_diagnosis$total_fascicle_vol_lost_nondep_bottom_3_quartiles)

@@

# geom violin within vs outside depression network, no cc
dep_net_group <- c(rep("Dep_net", times = 380), rep("Non_dep_net",times = 380))
net_values <- c(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_vol_lost_indepnet_top_quartile_no_cc, dep_and_healthy_groups_for_ICD_analysis$total_fascicle_vol_lost_nondep_bottom_3_quartiles_no_cc)

@@

dep_net_group <- c(rep("Dep_net", times = 380), rep("Non_dep_net",times = 380))
net_values <- c(dep_and_healthy_groups_for_ICD_analysis$prop_fascicle_vol_lost_indepnet_top_quartile, dep_and_healthy_groups_for_ICD_analysis$prop_fascicle_vol_lost_bottom_3_quartile)

@@

#p = 2.2 x 10^-16. 
violin_within_vs_outside_network_scaled_by_network_size <- ggplot(newdf_no_cc, aes(x=dep_net_group, y=net_values, fill=dep_net_group)) +
  geom_violin() +  
  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
  scale_x_discrete(labels=c("1" = "Dep Net", "2" = "Non-Dep Net")) + 
  ggtitle(paste0("Proportion Fascicle Volume Affected by Network")) +
  ylab("Proportion (tot volume lost/Net Vol) ") +
  ylim(0,0.1) + 
  theme(plot.title = element_text(size=16, hjust = 0.55),
        axis.text = element_text(size = 14, colour = "black"), axis.title.x = element_blank(), 
        axis.title.y = element_text(size=16),
        axis.line = element_line(size = 1.5, colour = "black", linetype=1),
        legend.position = "none",
        aspect.ratio=7/5,
        panel.background = element_rect(colour = "white", fill = "white"))
print(violin_within_vs_outside_network_scaled_by_network_size) #

@@

@@

#then, make the data frame
dep_and_healthy_groups_for_ICD_analysis <- df_demo_and_fascicle_volumes_full %>% 
  filter(depGroupVar != 0)  %>% 
  group_by(EMPI) %>% 
  arrange(EXAM_DATE) %>% 
  slice(1) %>% 
  ungroup()

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(visreg)
library(lme4)
library(lmerTest)
library(ggplot2)
library(reshape2)
library(pwr)
library(mgcv)
library(boot)
library(boot.pval)
library(lsr)
library(sjPlot)
#library(merTools)
#functions
source("~/BBL/msdepression/scripts/msdepression_functions.R")
```

@@

Current ns for people with at least 1 promis score= 
Total n promis scores: 1694-> 1813 
Total n unique individuals w/promis scores: 501->532

Different scores have different # of overall scans
(x<-promis_data[6:15] ; x[!is.na(x)] = 1; x[is.na(x)] = 0, colSums(x))

                  General_Health                  Quality_of_Life                  Physical_Health           Mental_Health_and_Mood 
                            1812                             1567                             1567                             1567 
  Social_Activities_Satisfaction   Carrying_Out_Social_Activities Carrying_Out_Physical_Activities               Emotional_Problems 
                            1567                             1565                             1563                             1563 
                 Fatique_Average     PostOp.PROMIS.Physical.Score 
                            1563                             1504

W/good mimosa:
Total n promis scores : 398 -> 412
Total n unique individuals w/promis scores: 116 -> 121
Total n unique indivs in nondepressed group = 36
Total n unique individuals in depressed group = 46->49

@@

Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
  1.0   396.0   800.5   933.8  1325.5  2606.0 
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
0.002747 1.087912 2.199176 2.565346 3.641484 7.159341

@@

Proportion:
Proportion within versus outside depression map correlated w/promis scores (33 analyses per group (11 promis domains x 3 networks [total, depression 25%, nondep 75%]))
    - all participants (121)
    - Depressed + nondepressed (85)
    - Non-depressed alone (36)
    - Depressed alone (49)

Proportion of individual fascicle affected related to promis scores (777 analyses per group (11 promis domains x 77 individual fascicles))
  - all participants (116)
  - Depressed + nondepressed (85)
  - Non-depressed alone (36)
  - Depressed alone (49)

@@

Volume within versus outside depression map correlated w/promis scores (33 analyses per group (11 promis domains x 3 networks [total, depression 25%, nondep 75%]))
   - all participants (121)
    - Depressed + nondepressed (85)
    - Non-depressed alone (36)
    - Depressed alone (49)

Volume of individual fascicle affected related to promis scores  (777 analyses per group (11 promis domains x 77 individual fascicles))
  - all participants (121)
  - Depressed + nondepressed (85)
  - Non-depressed alone (36)
  - Depressed alone (49)

Promis results:
Interestingly, across all 10 scores, with the exception of fatigue, Depressed patients have lower scores (lower = worse functioning), than non-depressed patients. controls. They all fdr correct. What I love about this is fatigue not being different. If fatigue was worse in depressed patients, one could argue that quality of life, health, emotional problems, social activities, etc are all worse because of underlying fatigue. Similarly, as fatigue is a component of the PHQ9 and depression screening, this could be confounding. That they were different in a lot of measures but not fatigue is informative.

Quality_of_Life	0.010			
Physical_Health	0.019			
Mental_Health_and_Mood	0.011		
Social_Activities_Satisfaction	0.001		
Carrying_Out_Social_Activities	0.007			
Carrying_Out_Physical_Activities	0.032			
Emotional_Problems	0.011			
Fatique_Average	0.181			
PostOp.PROMIS.Physical.Score	0.032			
PostOp.PROMIS.Mental.Score	0.001

Proportion
Proportion within versus outside depression map correlated w/promis scores - NO SIGNIFICANT FINDINGS
  - all participants (121)
  - Depressed + nondepressed (85)
  - Non-depressed alone (36)
  - Depressed alone (49)

Proportion of individual fascicle affected related to promis scores-  NO SIGNIFICANT FINDINGS
  - all participants (121)
  - Depressed + nondepressed (85)
  - Non-depressed alone (36)
  - Depressed alone (49)

Volume     
Volume within versus outside depression map correlated w/promis scores -  NO SIGNIFICANT FINDINGS
  - all participants (121)
  - Depressed + nondepressed (85)
  - Non-depressed alone (36)
  - Depressed alone (49)

Volume of individual fascicle affected related to promis scores-  NO SIGNIFICANT FINDINGS
  - all participants (121)
  - Depressed + nondepressed (85)
  - Non-depressed alone (36)
  - Depressed alone (49)

@@

##########################################################
#            Read in PROMIS Data              #
##########################################################
#promis_data <- readRDS(paste0(homedir, "/data/dac/promis_data_cleaned_n1694_unique_indiv_n501_2015-2022.rds"))
promis_data <- readRDS(paste0(homedir, "/data/dac/promis_data_20220824_fixed_physical_health_cleaned_n1813_unique_indiv_n532_2015-2022.rds"))
promis_score_names <- names(promis_data[7:16])

df_people_with_promis_data <- df_demo_and_fascicles %>%
  filter(EMPI %in% promis_data$EMPI) #n=416

unique_empis_in_promis_group <- unique(df_people_with_promis_data$EMPI) #n=121

```{r make_df_with_volume_instead_of_proportion}
#I'll read in the volume of each fascicle, and multiply it by the proportion of volume loss in each subject, thereby returing the volume of the fascicle affected

@@

just_fascicle_and_proportion <- fascicle_values_dep_no_cranial_nerves %>% dplyr::select(fascicle, prop_in_mask)

write.table(file = paste0(homedir, "/results/fascicle_proportion_overlap_with_depression_network_n77.csv"), x = just_fascicle_and_proportion, sep = ",", row.names = F, col.names = FALSE, quote=F)

@@

fascicle_volumes_dep_network_no_cranial_nerves <- fascicle_values_dep_no_cranial_nerves %>%
filter(fascicle%in% fascicle_names_no_cranial_nerves)

@@

#sort all the fascicles by %overlap, in decreasing order (so highest overlap at the top), and then take the top 1-quartile
dep_network_names_top_quartile_no_cranial_nerves_by_vol<- (fascicle_values_dep_no_cranial_nerves[order(fascicle_values_dep_no_cranial_nerves$non_zero_voxels_in_dep_map, decreasing = TRUE),])$fascicle[1:quartile] #n=19
write.table(dep_network_names_top_quartile_no_cranial_nerves_by_vol, file = paste0(homedir, "/results/dep_network_names_top_quartile_no_cranial_nerves_by_vol.txt"), quote = F, row.names = F, col.names = F)

dep_network_total_volume_top_quartile_no_cranial_nerves <-
sum(fascicle_volumes_dep_network_no_cranial_nerves$num_voxels_total[which(fascicle_volumes_dep_network_no_cranial_nerves$fascicle %in% dep_network_names_top_quartile_no_cranial_nerves_by_vol)])

@@

bottom_75_total_volume_no_cranial_nerves <-
sum(fascicle_volumes_dep_network_no_cranial_nerves$num_voxels_total[which(fascicle_volumes_dep_network_no_cranial_nerves$fascicle %in% dep_network_names_bottom_3_quartiles_no_cranial_nerves_by_vol)])

#### Calculate total volume in all non-cranial_nerve_network
total_volume_all_full_fascicles <- dep_network_total_volume_top_quartile_no_cranial_nerves + bottom_75_total_volume_no_cranial_nerves
#plot values within the depression network, and values outside of it

@@

dep_and_healthy_groups_for_ICD_analysis <- df_demo_and_fascicle_volumes_full %>% 
  filter(depGroupVar != 0)  %>% 
  mutate(total_fascicle_vol_lost = rowMeans(across(fascicle_names_no_cranial_nerves))) %>%
  mutate(sum_fascicle_vol_lost = rowSums(across(fascicle_names_no_cranial_nerves))) %>%
  mutate(proportion_volume_lost_per_total_network_size_sum = sum_fascicle_vol_lost/total_volume_all_full_fascicles) %>%

  mutate(total_fascicle_vol_lost_indepnet_top_quartile = 
           rowMeans(across(dep_network_names_top_quartile_no_cranial_nerves_by_vol))) %>%
  mutate(sum_fascicle_vol_lost_indepnet_top_quartile = 
           rowSums(across(dep_network_names_top_quartile_no_cranial_nerves_by_vol))) %>%
  mutate(prop_fascicle_vol_lost_indepnet_top_quartile = (total_fascicle_vol_lost_indepnet_top_quartile / dep_network_total_volume_top_quartile_no_cranial_nerves)) %>%
  mutate(proportion_volume_lost_dep_net_by_network_size_sum = sum_fascicle_vol_lost_indepnet_top_quartile /dep_network_total_volume_top_quartile_no_cranial_nerves) %>%

  mutate(total_fascicle_vol_lost_nondep_bottom_3_quartiles = 
           rowMeans(across(dep_network_names_bottom_3_quartiles_no_cranial_nerves_by_vol))) %>%
  mutate(sum_fascicle_vol_lost_nondep_bottom_3_quartiles = 
           rowSums(across(dep_network_names_bottom_3_quartiles_no_cranial_nerves_by_vol))) %>%
  mutate(prop_fascicle_vol_lost_bottom_3_quartile = (total_fascicle_vol_lost_nondep_bottom_3_quartiles / bottom_75_total_volume_no_cranial_nerves)) %>% 
   mutate(proportion_volume_lost_nondep_net_by_network_size_sum = sum_fascicle_vol_lost_nondep_bottom_3_quartiles /bottom_75_total_volume_no_cranial_nerves) %>%

  mutate(total_fascicle_vol_lost_no_cc = rowMeans(across(fascicle_names_no_cranial_nerves[fascicle_names_no_cranial_nerves!="CC"]))) %>%
  mutate(total_fascicle_vol_lost_indepnet_top_quartile_no_cc = 
           rowMeans(across(dep_network_names_top_quartile_no_cranial_nerves_by_vol[dep_network_names_top_quartile_no_cranial_nerves_by_vol != "CC"]))) %>%
  mutate(total_fascicle_vol_lost_nondep_bottom_3_quartiles_no_cc = 
           rowMeans(across(dep_network_names_bottom_3_quartiles_no_cranial_nerves_by_vol[dep_network_names_bottom_3_quartiles_no_cranial_nerves_by_vol != "CC"]))) %>%

  #remove people who didn't lose anything, i.e. bad data
 # filter(total_fascicle_vol_lost != 0) %>%
  group_by(EMPI) %>% 
  arrange(EXAM_DATE) %>% 
  slice(1) %>% 
  ungroup()

@@

### use sums instead of means
#wilcox test because non normally distributed; sums instead of means, scaled by network size p < 2.2*10^-16
msdisease_within_versus_outside_depression_network_sums_scaled_by_size_wilcoxon <- wilcox.test(dep_and_healthy_groups_for_ICD_analysis$proportion_volume_lost_dep_net_by_network_size_sum, dep_and_healthy_groups_for_ICD_analysis$proportion_volume_lost_nondep_net_by_network_size_sum,paired = TRUE)

#wilcox test because non normally distributed; sums instead of means, scaled by network size, only in non_dep people p < 2.2*10^-16
msdisease_within_versus_outside_depression_network_sums_scaled_by_size_wilcoxon_nondep <- wilcox.test(dep_and_healthy_groups_for_ICD_analysis$proportion_volume_lost_dep_net_by_network_size_sum[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1], dep_and_healthy_groups_for_ICD_analysis$proportion_volume_lost_nondep_net_by_network_size_sum[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1], paired = TRUE)

#wilcox test because non normally distributed; sums instead of means, scaled by network size, only in dep people p < 2.2*10^-16
msdisease_within_versus_outside_depression_network_sums_scaled_by_size_wilcoxon_dep <- wilcox.test(dep_and_healthy_groups_for_ICD_analysis$proportion_volume_lost_dep_net_by_network_size_sum[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2], dep_and_healthy_groups_for_ICD_analysis$proportion_volume_lost_nondep_net_by_network_size_sum[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2], paired = TRUE)

@@

#### interaction of diagnosis by network

scale=1

df_empi_dx_network_proportions <- dep_and_healthy_groups_for_ICD_analysis %>%
  mutate(subject = as.factor(EMPI)) %>%
  mutate(diagnosis = as.factor(depGroupVar)) %>%
  mutate(Dep_network = proportion_volume_lost_dep_net_by_network_size_sum) %>%
  mutate(Nondep_network = proportion_volume_lost_nondep_net_by_network_size_sum) %>%
  #mutate(Dep_network_affected = total_fascicle_vol_lost_indepnet_top_quartile) %>%
  #mutate(Nondep_network_affected = total_fascicle_vol_lost_nondep_bottom_3_quartiles) %>%
  dplyr::select(subject, diagnosis, Dep_network, Nondep_network) %>% 
  gather(network, proportion_affected, -subject, -diagnosis) %>% #this is like a melt. Keeps empi and depGroupVar out of the melt
 # mutate(network_size = ifelse(network == "Dep_network", dep_network_total_volume_top_quartile_no_cranial_nerves/scale, bottom_75_total_volume_no_cranial_nerves/scale)) %>%
#  mutate(total_affected_volume_in_net = (proportion_affected * network_size)) %>% 
  ungroup()

#df_empi_dx_network_proportions <- as.data.frame(df_empi_dx_network_proportions)

diagnosis_by_network_interaction_lmer <- lmer(proportion_affected ~ network*diagnosis + (1|subject), data = df_empi_dx_network_proportions)
summary(diagnosis_by_network_interaction_lmer)

diagnosis_by_network_interaction_lmer_main_effects <- lmer(proportion_affected ~ network+diagnosis + (1|subject), data = df_empi_dx_network_proportions)
summary(diagnosis_by_network_interaction_lmer_main_effects)

diagnosis_by_network_interaction_lmer_plot <- plot_model(diagnosis_by_network_interaction_lmer, type = "int")
print(diagnosis_by_network_interaction_lmer_plot)

#diagnosis_by_network_interaction_glmer <- glmer(cbind(total_affected_volume_in_net, network_size-total_affected_volume_in_net) ~ network*diagnosis + (1|subject), data = df_empi_dx_network_proportions, family = binomial(link="logit")) 
#summary(diagnosis_by_network_interaction_glmer )

#diagnosis_by_network_interaction_glmer_plot  <- plot_model(diagnosis_by_network_interaction_glmer , type = "int")
#print(diagnosis_by_network_interaction_glmer_plot)

#pred_df <- df_empi_dx_network_proportions %>% 
 #          dplyr::select(network,diagnosis) %>% 
  #         expand.grid() %>% distinct() %>% mutate(subject = rep(df_empi_dx_network_proportions$subject[1], 4))

#predicted_values_means_glmer <- predict(object=diagnosis_by_network_interaction_glmer,newdata=pred_df,se.fit=TRUE, re.form=NA, type = "response")

#predicted_values_means_lmer <- predict(object=diagnosis_by_network_interaction_lmer,newdata=pred_df,se.fit=TRUE, re.form=NA, type = "response")

#pred_lmer <- merTools::predictInterval(diagnosis_by_network_interaction_lmer, newdata =pred_df, n.sims = 999, which = "fixed")

#pred_glmer <- merTools::predictInterval(diagnosis_by_network_interaction_glmer, newdata = pred_df, n.sims = 999, which="fixed")

#pred_df_lmer_w_ci <- cbind(pred_df, pred_lmer)
#pred_df_glmer_w_ci <- cbind(pred_df, pred_glmer)

#plot_pred_df_lmer_plot <- ggplot(pred_df_lmer_w_ci,aes(x=network,y=fit,color=diagnosis, group=diagnosis, ymax=upr,ymin=lwr)) +
 #  geom_point(position = position_dodge(width=0.5),size=1) + geom_errorbar(size=1,position = position_dodge(width=0.5),width=.5)+geom_line(position = position_dodge(width=0.5),size=1) 
#  ylim(0.2,0.5)

#plot_pred_df_glmer_plot <- ggplot(pred_df_glmer_w_ci,aes(x=network,y=fit,color=diagnosis, group=diagnosis, ymax=upr,ymin=lwr)) +
   #geom_point() + geom_errorbar()+geom_line()

#geom_point(aes(color=diagnosis)) + geom_line(aes(color=diagnosis)) + geom_errorbar()

#ggplot(pred_df,aes(x=network,y=mean,color=diagnosis,ymax=upper_ci,ymin=lower_ci)) + geom_point() + geom_errorbar()+geom_line()
#predicted_values_ces <- predict(object=diagnosis_by_network_interaction_glmer,newdata=pred_df,se.fit=TRUE, re.form=NA)

#binomial, model needs to account for the fact that you can't have values outside of the 0-1 range. Change families because outcome variable not from a normal distribution.

@@

# geom violin within vs outside depression network
dep_net_group <- c(rep("Dep_net", times = dim(dep_and_healthy_groups_for_ICD_analysis)[1]), rep("Non_dep_net",times =dim(dep_and_healthy_groups_for_ICD_analysis)[1]))
net_values <- c(df_mean_fascicle_volumes_and_diagnosis$total_fascicle_vol_lost_indepnet_top_quartile, df_mean_fascicle_volumes_and_diagnosis$total_fascicle_vol_lost_nondep_bottom_3_quartiles)

@@

# geom violin within vs outside depression network, no cc
dep_net_group <- c(rep("Dep_net", times = dim(dep_and_healthy_groups_for_ICD_analysis)[1]), rep("Non_dep_net",times =dim(dep_and_healthy_groups_for_ICD_analysis)[1]))
net_values <- c(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_vol_lost_indepnet_top_quartile_no_cc, dep_and_healthy_groups_for_ICD_analysis$total_fascicle_vol_lost_nondep_bottom_3_quartiles_no_cc)

@@

dep_net_group <- c(rep("Dep_net", times = dim(dep_and_healthy_groups_for_ICD_analysis)[1]), rep("Non_dep_net",times =dim(dep_and_healthy_groups_for_ICD_analysis)[1]))
net_values <- c(dep_and_healthy_groups_for_ICD_analysis$prop_fascicle_vol_lost_indepnet_top_quartile, dep_and_healthy_groups_for_ICD_analysis$prop_fascicle_vol_lost_bottom_3_quartile)

@@

#p = 2.2 x 10^-16. 
violin_within_vs_outside_network_scaled_by_network_size <- ggplot(newdf_no_cc, aes(x=dep_net_group, y=net_values, fill=dep_net_group)) +
  geom_violin() +  
  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
  scale_x_discrete(labels=c("1" = "Dep Net", "2" = "Non-Dep Net")) + 
  ggtitle(paste0("Proportion Fascicle Volume Affected by Network")) +
  ylab("Proportion (mean tot volume lost/Net Vol) ") +
  ylim(0,0.1) + 
  theme(plot.title = element_text(size=16, hjust = 0.55),
        axis.text = element_text(size = 14, colour = "black"), axis.title.x = element_blank(), 
        axis.title.y = element_text(size=16),
        axis.line = element_line(size = 1.5, colour = "black", linetype=1),
        legend.position = "none",
        aspect.ratio=7/5,
        panel.background = element_rect(colour = "white", fill = "white"))
print(violin_within_vs_outside_network_scaled_by_network_size) #

#sums instead of means, scaling by size of network
dep_net_group <- c(rep("Dep_net", times = dim(dep_and_healthy_groups_for_ICD_analysis)[1]), rep("Non_dep_net",times =dim(dep_and_healthy_groups_for_ICD_analysis)[1]))
net_values <- c(dep_and_healthy_groups_for_ICD_analysis$proportion_volume_lost_dep_net_by_network_size_sum, dep_and_healthy_groups_for_ICD_analysis$proportion_volume_lost_nondep_net_by_network_size_sum)

#p = 2.2 x 10^-16. 
violin_within_vs_outside_network_sum_proportion_scaled_by_network_size <- ggplot(newdf_no_cc, aes(x=dep_net_group, y=net_values, fill=dep_net_group)) +
  geom_violin() +  
  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
  scale_x_discrete(labels=c("1" = "Dep Net", "2" = "Non-Dep Net")) + 
  ggtitle(paste0("Proportion Fascicle Volume Affected by Network")) +
  ylab("Proportion (sum total volume lost/Net Vol) ") +
 # ylim(0,0.1) + 
  theme(plot.title = element_text(size=16, hjust = 0.55),
        axis.text = element_text(size = 14, colour = "black"), axis.title.x = element_blank(), 
        axis.title.y = element_text(size=16),
        axis.line = element_line(size = 1.5, colour = "black", linetype=1),
        legend.position = "none",
        aspect.ratio=7/5,
        panel.background = element_rect(colour = "white", fill = "white"))
print(violin_within_vs_outside_network_sum_proportion_scaled_by_network_size) #

@@

#dfectine the depression network (all areas that intersect with depression network, no cranial nerves)
fascicle_proportions <- read.csv(paste0(homedir, "/results/fascicle_volumes_all_subjects_roi_n2336.csv"), header = T, sep = ",") #n = 2336

@@

#then, make the data frame
dep_and_healthy_groups_for_ICD_analysis <- df_demo_and_fascicle_volumes_full %>% 
  filter(depGroupVar != 0)  %>% 
  mutate(total_fascicle_vol_lost = rowMeans(across(fascicle_names_no_cranial_nerves))) %>%
#  filter(total_fascicle_vol_lost != 0) %>%
  group_by(EMPI) %>% 
  arrange(EXAM_DATE) %>% 
  slice(1) %>% 
  ungroup()
